Clustering Beat-Chroma Patterns\\ in a Large Music Database

### 2010-03-24 Paper/Paper.tex
basic properties fleshed out

\subsection{Basic Properties}
FIXME: flesh this out a \emph{little} more?

This section present some fundamental results of the clustering algorithm.
These are important, but do not change the larger picture. Due to space
constraints, we give few details and refer to the figures.
\begin{itemize}
\item Encoding performance improves with increasing training data. See Figure
\ref{fig:data_sizes}.
\item Encoding performance improves with increasing codebook size. See 
Table \ref{tab:cbsize}.
\item Larger patterns are more difficult to encode, thus requiring
larger codebooks. See Figure \ref{fig:perbeat}.
\end{itemize}

These properties are important to verify and for reproducing the experiments, 
but they are not surprising for a clustering algorithm.

>>>>

\subsection{Basic Properties}
This section present some fundamental results of the clustering algorithm.
None of the result appear surprising,  but they are important for 
reproducing the experiments.
\begin{itemize}
\item Encoding performance improves with increasing training data (Figure
\ref{fig:data_sizes}). Regarding the covergence of the performance,
we can imagine using $500$ or $1$K samples per codeword to learn if the
training set size is problematic.
\item Encoding performance improves with increasing codebook size
(Table \ref{tab:cbsize}). The increase seems significant, and
increasing the size of the codebook in an efficient way
is definitely part of our future work.
\item Larger patterns are more difficult to encode, thus requiring
larger codebooks. See Figure \ref{fig:perbeat}. The increase is steeper
until $4$ beats which usually corresponds to one bar.
\end{itemize}
